Enhance Image Classification Performance Via Unsupervised Pre-trained Transformers Language Models

### 2020-10-12 A-BasicCommom/CVPR2021/cvpr_classification.tex
1.CVPR v0.4.0, add a new paper: image classification draft.

\def\cvprPaperID{6666} % *** Enter the CVPR Paper ID here
\def\confYear{CVPR 2021}
%\setcounter{page}{4321} % For final version only

@@

%%%%%%%%% TITLE
\title{Lower Bounds on Rate of Convergence of Matrix Products in All-Pairs Shortest Path of Social Network}

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
  For the shortest path calculation task of all nodes in networks, Alon \etal~\cite{alon1997exponent} proposed an algorithm with matrix multiplication.
  In this paper, with the distance product association law and block matrix multiplication, all-pairs shortest path algorithm has a lowered time-bound of \(O(\log{n}2n^3)\).
  I propose an all-pairs shortest path algorithm that leveraging matrix sparseness judgment, convergence judgment, distance product matrix multiplication, distance product association law,
  scale-free characteristics of the social networks and limitation for floating-point operations on modern hardware, which has an improved lower time-bound \(O(14n^3)\).
  As an empirical study of social networks, I tested on movie actors' social network dataset, the proposed algorithm has an improvement of 39\% to 36.2 times in performance on CPU/GPU platforms comparing to Alon \etal's algorithm.
\end{abstract}

@@

In recent years, driven by Asian film industries such as China and India, the global box office has maintained a steady growth trend, and with the rapid development of social network applications, more and more actors use social networks for work communication.
Therefore, the social network has become an important tool for film distribution, marketing, promotion, and an important medium for film actors and fans to interact.
Previous studies have lacked research on actors' social networks, PageRank, an existing node influence algorithm, is not accurate in evaluating social network influence.
Social network feature measurement is an important task in social network data mining, some network characteristics, such as betweenness and closeness, need to calculate the distances between nodes.
As a result, efficient calculation of the shortest path is one of the key problems in social network measurement.
There was Floyd-Warshall~\cite{floyd1962algorithm,warshall1962theorem} algorithm for calculating node distances, Aho and Hopcroft~\cite{aho1974design} proved that distance product is homogenous to matrix multiplication,
Alon \etal~\cite{alon1997exponent} proposed an algorithm to calculate distance product by matrix multiplication, Zwick~\cite{zwick2002all} optimized distance product using fast matrix multiplication,
and Garbow and Winograd~\cite{garbow1985scaling} proposed an algorithm for distance product using matrix multiplication with element bound.
From time-bound of matrix multiplication, Strassen~\cite{strassen1969gaussian}, Coppersmith and Winograd~\cite{coppersmith1987matrix}, Davie and Andrew~\cite{davie2013improved}, Le Gall~\cite{le2014powers} proposed the block matrix multiplication with time-bound of \(O(n ^ {2.807})\), \(O(n^{2.376})\), \(O(n^{2.374})\), \(O(n^{2.373})\).
Lam \etal~\cite{lam1991cache} proposed that the progressive time complexity of matrix multiplication with a cache block size of $\Bbb B$ is \(O({2n^3 \over \Bbb B}+{n^2})\),
and Goto and Geijn~\cite{goto2008anatomy} proposed a new library, OpenBLAS, which has a higher cache hit rate and improved time cost in matrix computation on X86 CPU, compared to modern BLAS libraries, such as Intel MKL v8.1.1, ESSL v4.2.0, and ATLAS v3.7.11.
From point of view of matrix sparseness of network adjacent matrix, for sparse matrix multiplication, SciPy and CuPy use SciPy-sparse and CuPy-cuSparse to achieve efficient sparse matrix multiplication on CPU and GPU.
For dense matrix multiplication, NumPy, SciPy, CuPy, and ND4J use OpenBLAS, cuBLAS, and other libraries to achieve efficient block matrix multiplication on CPU and GPU.
Therefore, a feasible method for calculating the shortest path of full node pairs is: represents the network by adjacent matrix, then makes all matrix elements exponential, computes matrix multiplication, and finally takes the logarithm of matrix elements.
This procedure is called a distance product epoch.
Iterate several times to get all-pairs shortest path result.
Further, the analysis time complexity of the distance product calculation and iteration of each epoch.
For time complexity of distance product, matrix multiplication is the most complex sub-procedures;

\begin{enumerate}
\item For distance product optimization, Zwick proposed a distance product with block matrix multiplication, therefore choose proper computation device library with optimized cache for block matrix multiplication.
\item For iteration optimization, because Aho proved distance product is isomorphic to the matrix multiplication, and regard to that the distance product association law, optimize the iteration process by last distance product result reuse.
\end{enumerate}

@@

\section{Dataset And Hardware}
From January 1, 2011, to March 31, 2015, I collected the film actors' social network following relationship, profile information, and text message on Sina Weibo which is one of the popular social media in China.
In all, collected 8508 actors, 577775 edges, and 12526114 Sina Weibo posts.
I used a server with two Intel Xeon E5-2620 v4 CPUs and one NVIDIA GeForce GTX 1080 Ti GPU, in total 32 cores with a frequency of 2.1Ghz, 128G system memory, and 11G GPU memory in my experiment.

@@

\section{Comparison On Block Matrix Multiplication Implementtation}

@@

\section{Time-Bound Of Distance Product Algorithm With Cache Optimized Block Matrix Multiplication}

@@

\section{Shortest Path Algorithm With Block Matrix Multiplication}

Definition 1 (Outer Product Matrix Multiplication) Given matrices \(\Bbb A \in \Bbb R^{m*r}\), \(\Bbb B \in \Bbb R^{r*n}\) and \(\Bbb C \in \Bbb R^{m*n}\), the outer product is:
\begin{equation}
\Bbb C = \Bbb C  + \Bbb A(:,k)\bullet \Bbb B(k,:) , k \in (1,r)
\end{equation}

Given two vectors \(\textsc x\), \(\textsc y\), and matrix \(\Bbb A\), having \(\Bbb A \in \Bbb R^{m*n}\), \(\textsc x \in \Bbb R^{m}\) and \(\textsc y \in \Bbb R^{n}\) the outer product \(\bullet\) is defined by:
\begin{equation}
a_{ij} = a_{ij} + x_i * y_j, i \in (1,m), j \in (1,n)
\end{equation}

Definition 2 (Distance Product Matrix Multiplication) Given matrices \(\Bbb A \in \Bbb R^{m*r}\), \(\Bbb B \in \Bbb R^{r*n}\) and \(\Bbb C \in \Bbb R^{m*n}\), the distance product is:
\begin{equation}
  \Bbb C = \min(\Bbb C, \Bbb A(:,k)\odot \Bbb B(k,:)) , k \in (1,r)
\end{equation}

Given two vectors \(\textsc x\), \(\textsc y\), and matrix \(\Bbb A\), having \(\Bbb A \in \Bbb R^{m*n}\), \(\textsc x \in \Bbb R^{m}\) and \(\textsc y \in \Bbb R^{n}\) the distance product \(\odot\) is defined by:
\begin{equation}
a_{ij} = \min(a_{ij} , x_i + y_j), i \in (1,m), j \in (1,n)
\end{equation}
%-------------------------------------------------------------------------
\begin{figure*}
\begin{center}
  \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{figure1.pdf}}
\end{center}
   \caption{Adjacent matrix, each iterations and the result matrix visualization of actors' social network. (a) initial state after each round of calculation, (b) the result matrix after the first round of calculation, (c) the result matrix of the second round of calculation, (d) the third and in the same time last round of calculation, the all-pairs nodes shortest path result matrix.}
\label{fig:short}
\end{figure*}

@@

{\small
\bibliographystyle{ieee_fullname}
\bibliography{cpvr}
}

>>>>

\def\cvprPaperID{7777} % *** Enter the CVPR Paper ID here
\def\confYear{CVPR 2021}
%\setcounter{page}{4321} % For final version only

@@

%%%%%%%%% TITLE
\title{Enhance Image Classification Performance Via Unsupervised Pre-trained Transformers Language Models}

@@

%%%%%%%%% ABSTRACT
\begin{abstract}

  Image classification and categorization are essential for the capability of telling the difference between images for a machine.
  As \underline{B}idirectional \underline{E}ncoder \underline{R}epresentations from \underline{T}ransformers became popular in many tasks of natural language processing recent years,
  it is intuitive to use these pre-trained language models for enhancing the computer vision tasks, \eg image classification.
  In this paper, by encoding image pixels using pre-trained transformers, then connect to a fully connected layer,
  the classification model outperforms the Wide ResNet model and the linear-probe iGPT-L model,
  and achieved an accuracy of $97.72\%$\~$99.60\%$ on the CIFAR-10 image set, and an accuracy of $98.27\%$\~ on the CIFAR-100 image set.

\end{abstract}

@@

  Unsupervised pre-training is important in modern research of deep learning.
  Lee \etal~\cite{lee2009convolutional} used pre-training approaches
  in Computer Vision tasks in 2009, and later from 2010 to 2016, Nair and Hinton~\cite{nair2010rectified} proved that the pre-training process is supplementary in the CV tasks,
  thus, can be omitted in some cases.
  However, it started to flourish in natural language processing domain since Mikolov \etal~\cite{mikolov2013distributed} had proposed Word2Vec.
  Not long before Devin \etal~\cite{devlin2018bert}'s BERT language model dominates in most frequent used tasks in natural language processing,
  which is close resemble of Vicent \etal~\cite{vincent2008extracting}'s Denoising Autoencoder model, which was initially designed for images.
  Pre-training process become one of the most important procedures in deep learning.

@@

\section{Recent Work}

  Chen \etal~\cite{chen2020generative} trained image representation by sequence Transformers and tested on CIFAR-10 to show its outperforming to Wide-ResNet
which inspired from unsupervised natural language representation learning.
  Wang \etal~\cite{wang2019development} reviewed that convolutional neural networks had been proposed in 1960s, and had its implementation in 1980s,
and until LeCun \etal~\cite{lecun1990handwritten}'s first experiment on handwritten digit recognition, CNN's great potential had been revealed.
  In the 2010s, Krizhevsky \etal~\cite{krizhevsky2012imagenet} proposed the deep architecture, AlexNet, by concatenating multiple components of CNN layers.
Several years later, a lot of variants of AlexNet had been proposed by researchers and the accuracy of ImageNet had been greatly improved, \eg ZFNet~\cite{zeiler2014visualizing}, VGG~\cite{simonyan2014very}, GoogLeNet~\cite{szegedy2015going}, ResNet~\cite{he2016deep},
Wide-ResNet~\cite{zagoruyko2016wide}, ResNeXt~\cite{xie2017aggregated}, inception-ResNet-v2~\cite{szegedy2016inception}, DenseNet~\cite{huang2016deep}.
  Lu and Weng~\cite{lu2007survey} concluded that for multi-source image classification task, additional information such as signatures, texture, context and ancillary data can be combined to achieve better performance.
And it is difficult in handling the dichotomy between pixels and natural language texts in a single model.
  Cui \etal~\cite{cui2019pre, cui2020revisiting} proposed several whole-word-masking pre-trained Chinese language models,
which are improved versions of BERT~\cite{devlin2018bert} and RoBERTa~\cite{liu2019roberta} pre-trained language models, namely RBT3, RBTL3, and RoBERTa-wwm-ext-large.
These models achieved better performance in Chinese machine reading comprehension and Chinese document classification tasks.

@@

\section{Image Classification via Pre-trained Transformers Language Models}

@@

\section{Pre-trained Transformers Language Models}

@@

\section{Image Classification Model}

\begin{figure*}
\begin{center}
  \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{classification.pdf}}
\end{center}
   \caption{Concat, encoder, representation, and extraction layers for image classification task.}
\label{fig:short}
\end{figure*}

@@

{\small
\bibliographystyle{ieee_fullname}
\bibliography{cpvr_classification}
}
